\chapter{Introduction}
The development of efficient algorithms for solving large-scale mixed-integer programming (\MIP{}) problems has been a central focus of operations research for decades. Column generation, a powerful technique for solving large-scale linear programs, has been extended to integer programs through the branch-and-price algorithm. The effectiveness of branch-and-price relies heavily on the branching strategies employed and the ability to integrate various constraints into the master problem during column generation. However, these techniques introduce complexities that require careful management to ensure computational efficiency.

In this thesis, we explore advanced branching rules and constraints within the context of the branch-and-price framework, particularly focusing on the implementation and evaluation of the component bound branching rule. This rule, as proposed by Desrosiers et al. \cite{thebook}, offers a simpler alternative to Vanderbeck's generic branching scheme \cite{vanderbeck2011branching} by allowing for more flexible management of branching decisions within the master problem. The component bound branching rule provides an approach that is potentially easier to implement and integrate with modern solvers such as \GCG{}, yet it introduces challenges that necessitate modifications to the solver's architecture.

The foundational concepts of polyhedron representation and the primal simplex algorithm are introduced in Chapter \ref{ch:preliminaries}, providing the mathematical and algorithmic background necessary for understanding the core methods discussed later. In Chapter \ref{ch:cg_bp}, we delve into the specifics of column generation and branch-and-price, detailing the algorithms and their implementation, including the Dantzig-Wolfe reformulation, which serves as the basis for the decomposition approach used in branch-and-price.

Chapter \ref{ch:tools} provides a brief overview of the \SCIP{} Optimization Suite, with a particular focus on the \GCG{} solver, which forms the foundation for the implementation work carried out in this thesis. In Chapter \ref{ch:cmpbnd}, we present the component bound branching rule in detail, including its separation procedure and a theoretical comparison to Vanderbeck's generic branching scheme. This analysis sets the stage for a broader discussion on the limitations and advantages of different branching strategies in column generation.

One of the major contributions of this thesis is the introduction of a new interface within \GCG{} for handling constraints that exist solely within the master problem, termed \texttt{generic mastercuts}. These constraints, which do not have a direct counterpart in the original problem, require special handling within the solver, particularly with respect to synchronizing master variables across the search tree and applying dual value stabilization. Chapter \ref{ch:gm} begins by presenting the conceptual framework and definition of generic mastercuts, followed by an elaboration on the synchronization mechanisms and the application of dual value stabilization for these constraints, highlighting the technical innovations introduced in this thesis.

Chapter \ref{ch:implementation} focuses on the implementation aspects, detailing how the generic mastercut interface was integrated into \GCG{}, and how it supports the component bound branching rule and other advanced branching techniques.

The effectiveness of the component bound branching rule and the generic mastercut interface is rigorously evaluated in Chapter \ref{ch:evaluation}. We compare different separation heuristics and analyze the impact of dual value stabilization on the performance of the branching rule. Additionally, a detailed comparison with Vanderbeck's generic branching scheme provides insights into the conditions under which the component bound branching rule may offer advantages.

Finally, in Chapter \ref{ch:conclusion}, we conclude by summarizing the contributions of this thesis, reflecting on the broader implications of our findings for the field of operations research, and suggesting directions for future research. This thesis not only contributes to the theoretical understanding of advanced branching strategies but also provides practical tools for their implementation in state-of-the-art solvers, paving the way for more efficient solutions to complex integer programming problems.
