\documentclass[
	12pt, % Font size
	a4paper, % Paper size
	twoside, % Two-sided
]{report}

% Set the PDF version for LuaTeX
\usepackage{luacode}
\begin{luacode}
  pdf.setminorversion(6)
\end{luacode}

% Packages
\usepackage[english]{babel} % Set document language
\usepackage{pdfpages} % Include PDF files
\usepackage[utf8]{inputenc} % UTF-8 encoding (for umlauts etc.)
\usepackage[T1]{fontenc} % correct hyphenation
\usepackage{csquotes} % correct quotation marks
\usepackage{lmodern} % Computer Modern fonts
\usepackage{microtype} % better typesetting results (avoids underfull / overfull hboxes)
\usepackage{graphicx} % adding graphics
\usepackage{units} % typesetting units, e.g., \unit[10]{MB} and \unitfrac[100]{Mbit}{s}
\usepackage{booktabs} % publication quality tables
\usepackage{titlesec} % Customize chapter and section headings
\usepackage{setspace} % Set line spacing
\usepackage{geometry} % Set page margins
\usepackage{subcaption} % Subfigures
\usepackage{float} % Floats
\usepackage[
	backend=biber,
	style=numeric-comp,
	maxcitenames=2,
	natbib=false,
	sorting=none
]{biblatex} % Bibliography
\usepackage{hyperref} % Hyperlinks
\usepackage[super]{nth} % Superscript for numbers
\usepackage{amsmath} % Math symbols
\usepackage{amssymb} % Math symbols
\usepackage{mathtools} % Math symbols
\usepackage{amsthm} % Math symbols
\usepackage[
	ruled,
	linesnumbered,
	algochapter
]{algorithm2e} % Algorithms
\usepackage{bm} % Bold math symbols
\usepackage{tikz} % Drawing
\usepackage{tikz-qtree} % Drawing trees
\usepackage{etoolbox} % Patching
\usepackage{multicol} % Multiple columns
\usepackage{accents} % Math accentsdef
\usepackage[normalem]{ulem} % Underlining
\usepackage{etoolbox} % Patching
\usepackage{listings} % Code listings
\usepackage{bbm} % Blackboard bold
\usepackage{svg} % SVG images

\BeforeBeginEnvironment{algorithm}{\normalem}
\AfterEndEnvironment{algorithm}{\ULforem}

\usetikzlibrary{arrows.meta,positioning,shapes.multipart}

\setlength{\columnseprule}{1pt}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{2}

\svgsetup{inkscapepath=svgsubdir}

% Bibliography
\addbibresource{literature.bib}

\definecolor{bluekeywords}{rgb}{0.13,0.13,1}
\definecolor{greencomments}{rgb}{0,0.5,0}
\definecolor{redstrings}{rgb}{0.9,0,0}
\lstset{language=C,
	showspaces=false,
	showtabs=false,
	breaklines=true,
	showstringspaces=false,
	breakatwhitespace=true,
	escapeinside={(*@}{@*)},
	commentstyle=\color{greencomments},
	keywordstyle=\color{bluekeywords},
	stringstyle=\color{redstrings},
	basicstyle=\ttfamily,
	numbers=left,
	tabsize=3,
	frame=single,
}

% Custom Definitions
\input{definitions}

% Document
\begin{document}

\begin{titlepage}
	\centering
	{\Huge\bfseries Component Bound Branching in a Branch-and-Price Framework\par}
	\vspace{0.85cm}
	{\LARGE Master Thesis in Computer Science\\RWTH Aachen University\par}
	\vspace{2cm}
	{\LARGE Til Mohr\par}
	\vspace{0.5cm}
	{\large til.mohr@rwth-aachen.de\\Student ID: 405959\par}
	\vspace{2cm}
	{\large Aachen, \today\par}
	\vspace{2cm}
	\begin{minipage}{0.48\textwidth}
		\centering
		\nth{1} Examiner\\
		Prof. Dr. Peter Rossmanith\\
		Chair of Theoretical Computer Science\\
		RWTH Aachen University
	\end{minipage}
	\begin{minipage}{0.48\textwidth}
		\centering
		\nth{2} Examiner\\
		Prof. Dr. Marco Lübbecke\\
		Chair of Operations Research\\
		RWTH Aachen University
	\end{minipage}
\end{titlepage}

\cleardoublepage

% Acknowledgements
\section*{Acknowledgements}
I would like to express my sincere gratitude to my Professor and Supervisor, Prof. Lübbecke, for his guidance and support throughout this thesis. His expertise and valuable insights have been instrumental in shaping this work.

I would also like to thank Erik Mühmer for his assistance and support during the implementation phase in \GCG{}, providing valuable feedback and guidance.

Furthermore, I would like to extend my thanks to Oliver Gaul for the valuable discussions regarding some theoretical ideas.

Lastly, I would like to acknowledge Marc Ludevid Wulf for providing the inspiration to use unrolled linked lists to further improve the memory layout for the variable synchronization.

I am grateful to all the individuals mentioned above for their contributions and support, which have been crucial in the successful completion of this thesis.

\cleardoublepage


% Abstract
\begin{abstract}
This master thesis integrates the component bound branching rule, originally proposed by Vanderbeck et al. \cite{vanderbeck2010reformulation,vanderbeck1996exact} and later reformulated by Desrosiers et al. \cite{thebook}, into the branch-price-and-cut solver GCG. This rule, similarly to Vanderbeck's generic branching scheme \cite{vanderbeck2011branching}, exclusively operates within the Dantzig-Wolfe reformulated problem, where branching decisions generally have no corresponding actions in the original formulation. The current GCG framework requires modifications for such branching rules, especially within the pricing loop, as seen in Vanderbeck's method implementation. These rules also fail to utilize enhancements like dual value stabilization.

A significant contribution of this thesis is the enhancement of the GCG architecture to facilitate the seamless integration of new branching rules that operate solely on the reformulated problem. This allows these rules to benefit from current and future advancements in the branch-price-and-cut framework, including dual value stabilization, without necessitating alterations to the implementation of the branching rule itself.

The thesis proposes an interface to manage constraints in the master problem that lack counterparts in the original formulation. These constraints require specific modifications to the pricing problems to ensure their validity in the master. The \textbf{generic mastercut} interface, tightly integrated into the GCG solver, spans the pricing loop, column generation, and dual value stabilization. Enhancements to the existing branching rule interface complement this integration, enabling effective utilization of the generic mastercuts.

Finally, the component bound branching rule will be implemented using this new interface and evaluated on a set of benchmark instances. Its performance will be benchmarked against the existing Vanderbeck branching rule, offering a practical comparison of both approaches.
\end{abstract}

\cleardoublepage

% Table of contents
\tableofcontents
\cleardoublepage

% Chapters
\include{chapters/introduction/chapter}
\cleardoublepage
\include{chapters/preliminaries/chapter}
\cleardoublepage
\include{chapters/cg_bp/chapter}
\cleardoublepage
\include{chapters/tools/chapter}
\cleardoublepage
\include{chapters/cmpbnd/chapter}
\cleardoublepage
\include{chapters/gm/chapter}
\cleardoublepage
\include{chapters/implementation/chapter}
\cleardoublepage
\include{chapters/evaluation/chapter}
\cleardoublepage
\include{chapters/conclusion/chapter}
\cleardoublepage

% References
\normalem
\printbibliography
\ULforem

\end{document}

% End of document
\end{document}